Optimal design of experiment

### 2024-11-16 Sections/DOE.tex
16.11

	\begin{figure}[!h]
		\centering
		\resizebox{0.4\textwidth}{!}{%
			\begin{tikzpicture}
				% Ellipse parameters
				\def\ellipsecenter{(3,3)}
				\def\ellipseA{(0.75,5.25)} % End point for A-optimality arrow
				\def\ellipseB{(5.13,5.13)} % End point for E-optimality arrow
				\def\ellipseC{(4,1.2)}      % End point for D-optimality arrow

@@

	{\footnotesize 
		\begin{equation} 
			\begin{aligned} \Xi^* &= \arg \min_{ T^{\text{in}}(t), F(t) } \int_{t_0}^{t_f} \left[ - \ln j_D(\Xi, \dot{x}) + u(t)^\top R u(t) \right] dt \\ 
				\text{subject to} \quad & \dot{x} = G(x, t, \theta; \Xi), \\ 
				& t_0 = 0 \text{min} \\ 
				& t_f = 600 \text{min} \\ 
				& T^{0} = T^{\text{in}}(t=0), \\ 
				& P(t) \in \left\{100, 125, 150, 175, 200\right\} \text{bar}, \\ 
				%& R = \begin{bmatrix} 10^{-1} & 0 \ 0 & 10^{-2} \end{bmatrix}, \\ 
				%& u(t) = \begin{bmatrix} \dfrac{dF(t)}{dt} \ \dfrac{dT^{\text{in}}(t)}{dt} \end{bmatrix}, \\
				& 30^\circ\text{C} \leq T^{\text{in}}(t) \leq 40^\circ\text{C}, \\ 
				& 3.33 \cdot 10^{-5} \leq F(t) \leq 6.67 \cdot 10^{-5} 
				\end{aligned} 
				\label{EQ:Formulation_2} 
			\end{equation} }

>>>>

	\begin{figure}[!h]
		\centering
		\resizebox{0.8\columnwidth}{!}{%
			\begin{tikzpicture}
				% Ellipse parameters
				\def\ellipsecenter{(3,3)}
				\def\ellipseA{(0.75,5.25)} % End point for A-optimality arrow
				\def\ellipseB{(5.13,5.13)} % End point for E-optimality arrow
				\def\ellipseC{(4,1.2)}      % End point for D-optimality arrow

@@

	{\footnotesize 
		\begin{equation} 
			\begin{aligned} \Xi^* &= \arg \min_{ T^{\text{in}}(t), F(t) } \int_{t_0}^{t_f} \left[ - \ln j_D(\Xi, \dot{x}) + \frac{du(t)}{dt}^\top R \frac{du(t)}{dt} \right] dt \\ 
				\text{subject to} \quad & \dot{x} = G(x, t, \theta; \Xi), \\ 
				& t_0 = 0 \text{min} \\ 
				& t_f = 600 \text{min} \\ 
				& T^{0} = T^{\text{in}}(t=0), \\ 
				& P(t) \in \left\{100, 125, 150, 175, 200\right\} \text{bar}, \\ 
				& 30^\circ\text{C} \leq T^{\text{in}}(t) \leq 40^\circ\text{C}, \\ 
				& 3.33 \cdot 10^{-5} \leq F(t) \leq 6.67 \cdot 10^{-5} \\
				& R = \begin{bmatrix} 0.1 & 0 \\ 0 & 0.01 \end{bmatrix} \\ 
				& \frac{du(t)}{dt} = \begin{bmatrix} \dfrac{dF(t)}{dt} \\ \dfrac{dT^{\text{in}}(t)}{dt} \end{bmatrix}
				\end{aligned} 
				\label{EQ:Formulation_2} 
			\end{equation} }

### 2024-11-16 Sections/Results_DOE.tex
16.11

	For each pressure case, the profiles with the lowest value of the objective function are further analysed. As shown in Figure \ref{fig:profiles_T}, all the inlet temperature profiles follow the same pattern. Initally, the system starts from the highest temperature (upper control bound) and gradually decreasing to lowest temperatures (lower control bound).

>>>>

	For each pressure case, the profiles with the lowest value of the objective function are further analysed. As shown in Figure \ref{fig:profiles_T}, the dynamic behavior of the inlet temperature ($T^{in}$) for various cases in a supercritical CO2 extraction process. The initial temperature starts uniformly at $40~^\circ C$ for all cases but evolves differently depending on the operating conditions. These results underscore the sensitivity of supercritical CO$_2$ properties to control parameters such as temperature, particularly near the critical point. This observation aligns with the phenomenon that supercritical fluids exhibit properties like density and viscosity undergo strong non-linear changes around the critical point. At 200 bar the
